Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-19 article/article.tex
(+) Corr in article and continued slideshow

The simplest approch considers only the number of aircraft per sector $N_\text{aircraft}$. We
define two arbitary thresholds, namely $th_\text{low}$ and $th_\text{high}$, defining
three zones where the workload is low (resp.\ normal and high) if $N_\text{aircraft} < th_\text{low}$
(resp. $th_\text{low} \leq N_\text{aircraft} \leq th_\text{high}$ and $th_\text{high} < N_\text{aircraft}$).
Those workload levels are translated to probabilities $p_\text{low}$, $p_\text{normal}$ and
$p_\text{high}$, where $p_\text{low}(S)$ is the probability that the sector $S$ is underloaded
(resp.\ balanced and overloaded). In short, for a sector $S$ at time $t$ and $N_\text{aircraft}$:
\begin{equation}
  \begin{aligned}
    p_\text{low}^{S, t} &= \mathbb{1}_{[0, th_\text{low}]}(N_\text{aircraft}) \\
    p_\text{normal}^{S, t} &= \mathbb{1}_{[th_\text{low}, th_\text{high}]}(N_\text{aircraft})\\
    p_\text{high}^{S, t} &= \mathbb{1}_{[th_\text{low}, \infty[}(N_\text{aircraft})
  \end{aligned}
\end{equation}
where $\mathbb{1}$ is the indicator function defined by:
\begin{equation}
  \mathbb{1}_{I}(x) =
  \begin{cases}
    1 & \text{if\,} \quad x \in I\\
    0 & \text{otherwise}
  \end{cases}
\end{equation}

>>>>

The simplest approch considers only the number of aircraft per sector $N_\text{aircraft}$. We
define two arbitary thresholds, namely $th_\text{low}$ and $th_\text{high}$, defining
three zones where the workload is low (resp.\ normal and high) if $N_\text{aircraft} < th_\text{low}$
(resp. $th_\text{low} \leq N_\text{aircraft} \leq th_\text{high}$ and $th_\text{high} < N_\text{aircraft}$).
Those workload levels are translated to probabilities $p_\text{low}$, $p_\text{normal}$ and
$p_\text{high}$, where $p_\text{low}(S)$ is the probability that the sector $S$ is underloaded
(resp.\ balanced and overloaded). In short, for a sector $S$ at time $t$ and $N_\text{aircraft}$:
\begin{equation}
  \begin{aligned}
    p_\text{low}^{S, t} &= \mathbb{1}_{[0, th_\text{low}[}(N_\text{aircraft}) \\
    p_\text{normal}^{S, t} &= \mathbb{1}_{[th_\text{low}, th_\text{high}]}(N_\text{aircraft})\\
    p_\text{high}^{S, t} &= \mathbb{1}_{]th_\text{low}, \infty[}(N_\text{aircraft})
  \end{aligned}
\end{equation}
where $\mathbb{1}$ is the indicator function defined by:
\begin{equation}
  \mathbb{1}_{I}(x) =
  \begin{cases}
    1 & \text{if\,} \quad x \in I\\
    0 & \text{otherwise}
  \end{cases}
\end{equation}
